Need a good title.

### 2017-12-08 ms.tex
temp pushing ms

>>>>

\ml{$Z^{C}$ = $phyZ^{T}$ * Z}

The random-effect model matrix $Z$ can be decomposed into term-wise model matrix $Z_{i}$ as described in \ml{in text citation lme4}.
Thus, the phylogenetic correlated random-effect matrix $Z^{C}_{i}$ is

\begin{align}
Z^{C} & = BS Z ,
\end{align}

where $BS$ is an $b \times s$ matrix of branch--species relation.

\ml{for correlated intercept and slope it is $Z^{C} = Kron(BS,diag(repterm))^T * Z$}
